\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates in Figs

Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}. A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratio $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary number $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$. Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through \citep{guan_2003}, 
\begin{equation} 
   \mathcal{Q} = U_{f} b \lambda_{f}.\label{eqn:guaneqn} 
\end{equation} 
Numerical simulations performed with {\it VR} of 10 and 150 showed finger width of approximately 0.45-0.70 and \blue{XX (Jeff)} cm (Fig.~\ref{fig:homoheleshaw_VN10_VN250}), respectively. This is a close match with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates finger width ranging from 0.125 to 0.750 (depending on the tip velocity).

>>>>

Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}. A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratio $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary number $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$. Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through \citep{guan_2003}, 
\begin{equation} 
   \mathcal{Q} = U_{f} b \lambda_{f}.\label{eqn:guaneqn} 
\end{equation} 
Numerical simulations performed with {\it VR} of 10 and 150 showed finger width of approximately 0.45-0.70 and \blue{XX (Jeff)} cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150}), respectively. This is a close match with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates finger width ranging from 0.125 to 0.750 (depending on the tip velocity).

### 2017-06-29 Papers/ViscousInstabilities/article_figure1.tex
Updates in Figs

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
 \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}
       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}}
\caption{Simulated flow in a Hele-Shaw cell for viscosity ratio of 10 (left) and 150 (right \red{to be added}). \blue{ Jeff: Add comments here wrt to  tip width as a model validation wrt Saffmann's and  Guan's papers.} The domain contains $26313$ \PN[1]{2} triangular elements.}
\label{fig:homoheleshaw_VN10_VN250}
\end{figure}

>>>>

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
 \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}
       \includegraphics[width=.49\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D5003_k2b}}
\caption{Simulated flow in Hele-Shaw cells performed with viscosity ratios of 10 (left, t=7.61s) and 150 (t=1.94s). Width of largest fingers are approximetely 0.70 and 0.90cm, which are in good agreement with values obtained from \citet{guan_2003}'s analytic solution. Domains of both simulations contain $26313$ \PN[1]{2} triangular elements.}
\label{fig:homoheleshaw_VN10_VN150}
\end{figure}
